SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-01-27 paper_rl/paper.tex

The classification reward metric (\autoref{eq:R_classification}) captures how correct the classifier is on average for all future packets of a flow. The label of each packet in a flow has a value of 0 for non-attack traffic and 1 for attack traffic with one flow being only attack or non-attack but not mixed. The confidence is the sigmoided ($\frac{e^x}{1+e^x}$) output of the classifier, yielding a value between 0 and 1, where 0 is absolute confidence for a flow being benign and 1 is absolute confidence for a flow being an attack. 
\begin{align}
\begin{split}
R_{\text{classification},t} = \frac{1}{T-t} \sum_{i=t+1}^{T} |\text{label}_i - \text{confidence}_i|
\end{split}
\label{eq:R_classification}
\end{align}

>>>>

The classification reward metric (\autoref{eq:R_classification}) captures how correct the classifier is on average for all future packets of a flow. The label of each packet in a flow has a value of 0 for non-attack traffic and 1 for attack traffic with one flow being only attack or non-attack but not mixed. The confidence is the sigmoided $\left(\frac{e^x}{1+e^x}\right)$ output of the classifier, yielding a value between 0 and 1, where 0 is absolute confidence for a flow being benign and 1 is absolute confidence for a flow being an attack.
\begin{align}
\begin{split}
R_{\text{classification},t} = \frac{1}{T-t} \sum_{i=t+1}^{T} |\text{label}_i - \text{confidence}_i|
\end{split}
\label{eq:R_classification}
\end{align}
